---
title: "test_easy_markdown"
author: "Haris Zafeiropoulos"
date: '`r Sys.Date()`'
output:
  html_document: 
    keep_md: yes
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(tinytex.verbose = TRUE)

```

## Compile and run VolEsti. Use the R extension to visualize sampling in a polytope.

Here are the libraries needed

```{r libraries}
options(tinytex.verbose = TRUE)
library(ggplot2)
library(volesti)
```




### keep a polytope as a variable after reading a .ine file 

```{r pressure, echo=TRUE}
options(tinytex.verbose = TRUE)
polytope = file_to_polytope("/home/haris/volume_approximation/R-proj/inst/extdata/cross_10.ine")
```



### random sampling with different algorithms 

```{r sampling, echo=TRUE}
options(tinytex.verbose = TRUE)
points_cdhr =  sample_points(P = polytope, n = 5000, distribution = list("density" = "uniform"),  random_walk = list("walk"="CDHR"))
points_rdhr =  sample_points(P = polytope, n = 5000, distribution = list("density" = "uniform"),  random_walk = list("walk"="RDHR"))
points_biw =  sample_points(P = polytope, n = 5000, distribution = list("density" = "uniform"),  random_walk = list("walk"="BiW"))
points_baw =  sample_points(P = polytope, n = 5000, distribution = list("density" = "uniform"),  random_walk = list("walk"="BaW"))
```


### keep sample points 

```{r sample points}
options(tinytex.verbose = TRUE)
BaW = data.frame(x=points_baw[1,], y=points_baw[2,])
BiW = data.frame(x=points_biw[1,], y=points_biw[2,])
CDHR = data.frame(x=points_cdhr[1,], y=points_cdhr[2,])
RDHR = data.frame(x=points_rdhr[1,], y=points_rdhr[2,])

```


### bind all the points in a dataframe
```{r bind}
options(tinytex.verbose = TRUE)
walks = rbind(BaW,BiW,CDHR,RDHR)
```


### add a column in the dataframe to tag the points of each algorithm
```{r tag}
walks$random_walk = c(rep("BaW",5000),rep("BiW",5000),rep("CDHR",5000),rep("RDHR",5000)) 
```



### plot it 
```{r plot}
ggplot(walks, aes(x=x, y=y, group=random_walk,col=random_walk)) + 
  geom_point() + geom_smooth() + labs(title = "uniform sampling on cross_10.ine file / H-polytope")
```




### more sampling, more plots

```{r more_sampling_1}
P = gen_cube(2, 'H')
p=sample_points(P, n=2000, random_walk = list("walk" = "BiW", "walk_length" = 1))
r = t(p)
q = as.data.frame(r)

```


```{r more_plots_1}

names(q)[1]='x'
names(q)[2]='y'
ggplot(q, aes(x=x,y=y)) +
       geom_point() + geom_smooth()


```


### Get sample points from the inside of polytope.
```{r more_sampling_2}
P = gen_rand_hpoly(2,17, seed=1917)
p=sample_points(P, n=2000, random_walk = list("walk" = "RDHR", "walk_length" = 1))
r = t(p)
q1 = as.data.frame(r)

```


```{r more_plots_2}
names(q1)[1]='x'
names(q1)[2]='y'
ggplot(q1, aes(x=x,y=y)) +
       geom_point() + geom_smooth()

```



### Get boundary points from the same polytope.
```{r more_sampling_3}
p=sample_points(P, n=2000, random_walk = list("walk" = "BRDHR", "walk_length" = 1))
r = t(p)
q2 = as.data.frame(r)

```


```{r more_plots_3}

names(q2)[1]='x'
names(q2)[2]='y'
ggplot(q2, aes(x=x,y=y)) +
       geom_point() + geom_smooth()

```


### and together..
```{r final_plot}

final_points=rbind(q1,q2)
final_points$random_walk = c(rep("RDHR",2000), rep("BRDHR",2000))

ggplot(final_points, aes(x=x, y=y, group=random_walk,col=random_walk)) + 
  geom_point() + geom_smooth() + labs(title = "in and out random walks")
```
